%!TEX root = ../thesis.tex
The first part of this report has given an overview of AngularJS and its core principles and features. The chapters work only as an introduction to the development of AngularJS applications and it is advised to have a closer look at the official documentation and the provided examples to get a more in-depth understanding of the framework.

The implementation of the XBMCMagic remote has shown that an entire app can be written by mostly using built-in directives and only providing application-specific services. Reducing the amount of custom code and relying on AngularJS's core features was a great way to learn AngularJS by heart because it reduced the amount of effort that would normally be put into trying to make a new framework work like other frameworks that have already been used. Furthermore, it has shown that AngularJS works well in mobile environments, even when used in a packaged hybrid application.

Collection.do however is a good example of a more complex AngularJS app that shares data across scopes, that has many different controllers and inherited scopes and that uses a service layer to interact with a backend. Most AngularJS examples in the official documentation only focus on one specific feature of an application and it is tough to find documentation on how to build more complex applications. Collection.do is a good example for exactly such an appliaction. In addition to that, the application uses and describes AngularJS features like repeaters, filters and many of the built-in directives that were not covered in the basic overview of AngularJS in this report.